---
title: "In-class Exercise 4"
author: "Wong Kelly"
date: "30 January 2023"
date-modified: "`r Sys.Date()`"
execute: 
  eval: true
  echo: true
  warning: false
editor: visual
---

## 1. Installing and Loading the R packages

```{r}
pacman::p_load(maptools, sf, raster, spatstat, tmap)
```

Things to learn from this code chunk. All explanations have to be outside the code chunk if not will encounter issues

## 2. Importing the Spatial Data

Always check the file by right clicking and check the projection system the dataset file is using

```{r}
childcare_sf <- st_read("data/child-care-services-geojson.geojson") %>%
  st_transform(crs = 3414)
```

```{r}
sg_sf <- st_read(dsn = "data", layer="CostalOutline")
```

```{r}
mpsz_sf <- st_read(dsn = "data", 
                layer = "MP14_SUBZONE_WEB_PL")
```

### 4.5.1 Converting sf data frames to sp's Spatial\* class

```{r}
childcare <- as_Spatial(childcare_sf)
mpsz <- as_Spatial(mpsz_sf)
sg <- as_Spatial(sg_sf)
```

```{r}
childcare

```

### 4.5.2 Converting the Spatial\* class into generic sp format

```{r}
childcare_sp <- as(childcare, "SpatialPoints")
sg_sp <- as(sg, "SpatialPolygons")
```

### 4.5.3 Converting the generic sp format into spatstat's ppp format

Convert to only x y coordinate in two columns form so that can use in analytics later on

```{r}
childcare_ppp <- as(childcare_sp, "ppp")
childcare_ppp
```
